Seshadri constants of curve configurations on surfaces

### 2024-07-18 sc-curve-config.tex
Final Changes before publication
Page 2 line 4: Replaced X and L with P^2 and O(1)

	On the other hand, when the points $x_1, \cdots, x_r$ lie in special position, the corresponding  Seshadri constant is frequently rational, and it is a very interesting problem to compute it. For example, if the points are collinear then 
	$\varepsilon(X,L,x_1,\ldots,x_r) = \frac{1}{r}$.

@@

 \subsection*{Acknowledgements} We thank the referee for a careful reading of the paper, pointing out some corrections and giving several useful suggestions which substantially improved the paper. The first author is partially supported by a grant from Infosys Foundation.

>>>>

	On the other hand, when the points $x_1, \cdots, x_r$ lie in special position, the corresponding  Seshadri constant is frequently rational, and it is a very interesting problem to compute it. For example, if the points are collinear then 
	$\varepsilon(\mathbb{P}^2,\mathcal{O}_{\mathbb{P}^2}(1),x_1,\ldots,x_r) = \frac{1}{r}$.

@@

 \subsection*{Acknowledgements} The first author is partially supported by a grant from Infosys Foundation.
